Cooperative Decision Making for Communities of Autonomous Web Services

### 2013-12-12 proposal/presentation/ekpresentation/ehsan_presentation.tex
changes

\begin{frame}{Presentation Outline}
    \begin{itemize}
     	\itemsep=.5cm
    	\item {\bf Introduction}
    	\item Background and Literature Review
    	\item Proposed Research
        \item Contributions and Research Activities
    	\item Time Line
    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame3 introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%\section{Motivation}
\subsection{Motivation}
    \begin{frame}{Motivation}
    \begin{itemize}
        \item High reliance on web services, created high competition and great business opportunities for online service developers
        \item Community goals:
        \begin{itemize}
            \item \textbf{User satisfaction, Service quality, high availability and responsiveness}.
            \item \textbf{Web Service Discovery over Internet}.
        \end{itemize}
    \end{itemize}
    \begin{figure}[htbp]
        \centering
        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
        \includegraphics[width=1.0 \columnwidth]{figures/figure7.png}
        %%\includegraphics[scale=0.5]{figure1}
        %\caption{The NetBill payment protocol} \label{figure7}
    \end{figure}
    \end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Problems and Research Questions}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Background}
\begin{frame}{Presentation Outline}
    \begin{itemize}
     	\itemsep=.5cm
    	\item Introduction
    	\item {\bf Background and Literature Review}
    	\item Proposed Research
        \item Contributions and Research Activities
    	\item Time Line
    \end{itemize}
\end{frame}

@@

    \begin{definition} [Shapley Value]\label{dfn:shapleyvalue}
        Given a coalitional game $(N,v)$, the Shapley value of player $i$ is given by: \\
        $\phi_i(N,v) = \sum_{S \subseteq N \backslash \left\{i\right\} } \frac{|S|! (|N|-|S|-1)!}{|N|!} (v(S \cup \left\{i\right\}) - v(S))$
    \end{definition}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Some properties}
    \begin{itemize}
        \item The core may not always be non-empty
        \item Shapley value always exists and is unique.
        \item When the valuation function is {\color{red}superadditive}, the Shapley value is {\color{red}individually rational}, i.e., it is an imputation.
        \item When the valuation function is {\color{red}convex}, the Shapley value is also group rational, hence, it is in the {\color{red}core}.
        \item A convex game has a non-empty core
        \item There are other well-known solution concepts: The bargaining set, The nucleolus and The nucleolus.
    \end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{$\epsilon$-Core}
    \begin{itemize}
        \item The core may not always be non-empty       
        \item (To add some items)
    \end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Coalition Structures}
    \begin{itemize}
        \item To reach a stable partition having many coalitions. 
        \item (To add some items)       
    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Proposed Research}
\begin{frame}{Presentation Outline}
    \begin{itemize}
     	\itemsep=.5cm
    	\item Introduction
    	\item Background and Literature Review
    	\item {\bf Proposed Research}
        \item Contribution and Research Activities
    	\item Time Line
    \end{itemize}
\end{frame}

@@

\begin{frame}{Problem Formulation and Modeling}
    \begin{itemize}
        \item Communities are robust service providers with well established market share and reputation
        \item The community is characterized by a request rate $R_C$
        \item Web services can perform tasks with some throughput rate ($Th_{ws}$)
        \item Web services come with different values of $QoS_{ws}$ for different metrics.
        \item 123
    \end{itemize}    
\end{frame}

@@

    \begin{itemize}
        \item A typical WS community, where web services can join or leave
        \item $v(C) = out(C)$
        \item Membership decision in made based on throughput and QoS of the web services.
        \item Community master needs to get quality web services to keep community stable, so other web services have no incentive to leave.

@@

\begin{frame}{Scenario One: Web Services and One Community}
    \begin{itemize}
        \item 123123
        \item 123123
        \item 123123
    \end{itemize}
    \begin{figure}[htbp]
        \centering
        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
        \includegraphics[width=0.8 \columnwidth]{figures/scenario2.png}
        %%\includegraphics[scale=0.5]{figure1}
        %\caption{The NetBill payment protocol} \label{figure7}
    \end{figure}

\begin{frame}{Continue: Desiderata of Paradoxes}
 \begin{enumerate}
\vspace{0.2cm} \item [P3.][\textbf{Committing everything known
from others}]
$ K_i K_j \varphi \Rightarrow C_{j \rightarrow i} \varphi$ such that $ i \neq j$.

\textbf{Meaning:} An agent (the debtor) commits toward another
agent (the creditor) to bring about what the creditor knows about
the debtor's knowledge.\\
\textbf{Example 3:}\\
$K_{Cus} K_{Mer}$ $deliverGoods \Rightarrow$ $C_{Mer \rightarrow Cus}$
$deliverGoods$.

\vspace{0.2cm} \item [P4.][\textbf{Knowing about his own
commitment}]

$C_{i\rightarrow j} \varphi \Rightarrow K_i (C_{i\rightarrow j}
\varphi) $ where $i \neq j$.

\textbf{Meaning:} An agent knows about his commitment.

\textbf{Example 4:}\\
$C_{Cus \rightarrow Mer}$ $sendPayment $ $\Rightarrow K_{Cus}$ $(C_{Cus \rightarrow Mer}$ $sendPayment)$.
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Continue: Desiderata of Paradoxes}

\begin{figure}[htbp]
    \begin{center}
%\includegraphics[width=10cm, height=5cm]{figures/figure2.eps}
    \includegraphics[width=.75 \columnwidth]{figures/figure2.png}
   % \caption{Model 1} \label{figure2}
    \end{center}
    \end{figure}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Continue: Desiderata of Paradoxes}
\begin{enumerate}
\vspace{0.2cm} \item [P5.][\textbf{Knowing the content of his own
fulfilled commitment}]

$Fu (C _{i\rightarrow j} \varphi) \Rightarrow K _i \varphi$ where
$i \neq j$.

\textbf{Meaning:} An agent knows the content of his fulfilled
commitment.\\
\textbf{Example 5:}\\
$Fu (C _{Cus\rightarrow Mer} sendPayment) \Rightarrow K_{Cus}$ $sendPayment$.
\begin{figure}[htbp]
    \begin{center}
%\includegraphics[width=10cm, height=5cm]{figures/figure2.eps}
    \includegraphics[width=.75 \columnwidth]{figures/figure3.png}
   % \caption{Model 2} \label{figure3}
    \end{center}
    \end{figure}

\end{enumerate}     	
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame23 Proposed Research %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

 \begin{frame}{Continue: Desiderata of Paradoxes}
 \begin{enumerate}

\vspace{0.2cm} \item [P6.][\textbf{Knowing the content of the
other's fulfilled commitment}]

$Fu (C _{i\rightarrow j} \varphi) \Rightarrow K_j \varphi$ where
$i \neq j$.

\textbf{Meaning:} The creditor knows the content of the debtor's
fulfilled commitment.\\
\textbf{Example 6:}\\
$ Fu (C_{cust \rightarrow Mer}$ $sendPayment)$ $\Rightarrow $ $k_{Mer} sendPayment$.
	\begin{figure}[htbp]
\begin{center}
%\includegraphics[width=12cm, height=5cm]{figures/figure4.eps}
\includegraphics[width=.70 \columnwidth]{figures/figure4.png}
%\caption{Model 3} \label{figure4}
\end{center}
\end{figure}
\end{enumerate}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame24 Proposed Research %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Continue: Desiderata of Paradoxes}
\begin{enumerate}
    \vspace{0.2cm} \item [P7.][\textbf{Knowing the commitment of the
other}]

$C_{i\rightarrow j} \varphi \Rightarrow AF K_j (C_{i\rightarrow j}
\varphi) $ where $i \neq j$.

\textbf{Meaning:} An agent should be aware of any commitments
directed towards him.\\
\textbf{Example 7:}\\
$C_{Mer \rightarrow Cus}$ $deliverGoods$ $\Rightarrow $ $AF K_{Cus}(C_{Mer \rightarrow Cus}$
$deliverGoods$).
\begin{figure}[htbp]
\centering
\includegraphics[width=.50 \columnwidth]{figures/figure5.png}
%\includegraphics[width=12cm, height=7cm]{figures/figure5.eps}
%\includegraphics[scale=0.5]{figure4.eps}
%\caption{Model 4} \label{figure5}
\end{figure}

\end{enumerate}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Continue: Desiderata of Paradoxes}
\begin{enumerate}
    \vspace{0.2cm} \item [P8.][\textbf{Knowing the fulfillment of his
own commitment}]

$Fu(C _{i\rightarrow j} \varphi) \Rightarrow K_i Fu(C
_{i\rightarrow j} \varphi)$ where $i \neq j$.

\textbf{Meaning:} The agent knows that he fulfills his commitment.\\
\textbf{Example 8:}\\
$Fu(C_{Cus\rightarrow Mer} sendPayment)\Rightarrow K_{Cus}Fu(C_{Cus \rightarrow Mer} sendPayment)$.

\vspace{0.2cm} \item [P9.][\textbf{Knowing the fulfillment of the
debtor's commitment}]

$Fu(C _{i\rightarrow j} \varphi) \Rightarrow K_j Fu(C_{i\rightarrow j} \varphi)$ where $i \neq j$.

\textbf{Meaning:} The creditor knows that the debtor fulfills his
commitment.\\
\textbf{Example 9:}\\
$Fu(C_{Cus \rightarrow Mer} sendPayment)\Rightarrow K_{Mer} Fu(C_{Cus \rightarrow Mer} sendPayment)$.
\end{enumerate}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame25 outline page %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{CTLKC properties}
\begin{frame}{CTLKC properties}
In addition to the properties of knowledge (in CTLK) and commitments (in CTLC), those properties hold in CTLKC:
\begin{enumerate}

\vspace{0.2cm} \item [Prop 1.] $C_{i \rightarrow j}\varphi
\Rightarrow \varphi$ is satisfiable but not valid.
\vspace{0.2cm} \item [Prop 2.] $C_{i \rightarrow j}\varphi
\Rightarrow K_i \varphi$ is satisfiable but not valid.
\vspace{0.2cm} \item [Prop 3.] $(C_{i \rightarrow j}\varphi \wedge
K_i (\varphi \Rightarrow \psi)) \Rightarrow C_{i \rightarrow j}
\psi$ is valid.
\vspace{0.2cm} \item [Prop 4.] $(C_{i \rightarrow j}(\varphi
\Rightarrow \psi) \wedge K_i \varphi) \Rightarrow C_{i \rightarrow
j} \psi$ is valid.
\vspace{0.2cm} \item [Prop 5.] $(C_{i \rightarrow j}\varphi \wedge
K_j (\varphi \Rightarrow \psi)) \Rightarrow C_{i \rightarrow j}
\psi$ is satisfiable but not valid.
\vspace{0.2cm} \item [Prop 6.] $(C_{i \rightarrow j}(\varphi
\Rightarrow \psi) \wedge K_j \varphi) \Rightarrow C_{i \rightarrow
j} \psi$ is satisfiable but not valid

\end{enumerate}
\end{frame}

\section{Research Activities}
\begin{frame}{Contribution and Research Activities}
    \begin{itemize}
     	\itemsep=.5cm
    	\item Introduction
    	\item Background and Literature Review
    	\item Proposed Research
        \item {\bf Contribution and Research Activities}
    	\item Time Line
    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame26 Contribution and Research Activities %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Contributions}
    \begin{frame}{Contributions}

    \begin{itemize}
     \itemsep=.35cm
     \item A new combined temporal logic, called CTLKC, that combines both CTLK and CTLC logics is introduced.
     \item This logic served as a language to express a set of rules that are used to reason about the interaction between knowledge and social commitments.
     \item Selection criteria are proposed to capture such reasoning rules.
     \item Nine paradoxes are recognized in CTLKC logic that should be addressed in any consistent logic combining knowledge and commitments.
     \item Six properties are identified and should be met in any logic combining knowledge and commitments.
        \end{itemize}

    \end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame27 Contribution and Research Activities

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame30 outline page
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Milestones}
\begin{frame}{Milestones}
    \begin{itemize}
     	\itemsep=.5cm
    	\item Introduction
    	\item Background and Literature Review
    	\item Proposed Research
        \item Contribution and Research Activities
    	\item {\bf Time Line}
    \end{itemize}
\end{frame}

>>>>

\begin{frame}{Presentation Outline}
    \begin{itemize}
     	\itemsep=.5cm
    	\item {\bf Introduction}
    	\item Background and Literature Review
    	\item Proposed Research
    	\item Time Line
    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame3 introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%\section{Motivation}
\subsection{Motivation}
    \begin{frame}{Motivation}
    \begin{itemize}
        \item High reliance on web services, created high competition and great business opportunities for online service developers
        \item Community goals:
        \begin{itemize}
            \item \textbf{User satisfaction, Service quality, high availability and responsiveness}.
            \item \textbf{Web Service Discovery over Internet}.
        \end{itemize}
    \end{itemize}
    \begin{figure}[htbp]
        \centering
        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
        %\includegraphics[width=1.0 \columnwidth]{figures/figure7.png}
        %%\includegraphics[scale=0.5]{figure1}
        %\caption{The NetBill payment protocol} \label{figure7}
    \end{figure}
    \end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Problems and Research Questions}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Background}
\begin{frame}{Presentation Outline}
    \begin{itemize}
     	\itemsep=.5cm
    	\item Introduction
    	\item {\bf Background and Literature Review}
    	\item Proposed Research
    	\item Time Line
    \end{itemize}
\end{frame}

@@

    \begin{definition} [Shapley Value]\label{dfn:shapleyvalue}
        Given a coalitional game $(N,v)$, the Shapley value of player $i$ is given by: \\
        $\phi_i(N,v) = \sum_{S \subseteq N \backslash \left\{i\right\} } \frac{|S|! (|N|-|S|-1)!}{|N|!} (v(S \cup \left\{i\right\}) - v(S))$
    \end{definition}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Some properties}
    \begin{itemize}
        \item The core may not always be non-empty
        \item Shapley value always exists and is unique.
        \item When the valuation function is {\color{red}superadditive}, the Shapley value is {\color{red}individually rational}, i.e., it is an imputation.
        \item When the valuation function is {\color{red}convex}, the Shapley value is also group rational, hence, it is in the {\color{red}core}.
        \item A convex game has a non-empty core
        \item There are other well-known solution concepts: The bargaining set, The nucleolus and The nucleolus.
    \end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{$\epsilon$-Core}
    \begin{itemize}
        \item The core may not always be non-empty
        \item (To add some items)
    \end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Proposed Research}
\begin{frame}{Presentation Outline}
    \begin{itemize}
     	\itemsep=.5cm
    	\item Introduction
    	\item Background and Literature Review
    	\item {\bf Proposed Research}
    	\item Time Line
    \end{itemize}
\end{frame}

@@

\begin{frame}{Problem Formulation and Modeling}
    \begin{itemize}
        \item Communities are robust service providers with well established market share and reputation
        \item The community is characterized by a request rate $R_C$
        \item Web services can perform tasks with some throughput rate ($Th_{ws}$)
        \item Web services come with different values of $QoS_{ws}$ for different metrics.
    \end{itemize}
\end{frame}

@@

    \begin{itemize}
        \item A typical WS community, where web services can join or leave
        \item $v(C) = Out(C)$
        \item Membership decision in made based on throughput and QoS of the web services.
        \item Community master needs to get quality web services to keep community stable, so other web services have no incentive to leave.
    \end{itemize}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Scenario One: Web Services and One Community}

    \begin{itemize}
        \item Upon receiving membership request the master web service checks if the coalition will be stable having the new member.
        \item If the game is convex, core exists.
        \item If the game is convex, Shapley value is in core.
        \item Convexity Condition:
        \begin{center}          
          $\forall S,T | S \subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in N,$ \\
          $v(S \cup \left\{i\right\}) - v(S) \leq v (T \cup \left\{i\right\}) - v(T)$ \\
          $\Leftrightarrow$  \\
          $v(S' \cup T') \geq v(S') + v(T') - v(S' \cap T')$            
        \end{center}
    \end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Scenario One: Web Services and One Community}

    \begin{figure}[htbp]
        \centering
        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
        \includegraphics[width=0.92 \columnwidth]{figures/dp.png}
        %%\includegraphics[scale=0.5]{figure1}
        %\caption{The NetBill payment protocol} \label{figure7}
    \end{figure}

    \begin{itemize}
        \item Approximation of the optimum result for each level, is it possible?
    \end{itemize}

@@

\begin{frame}{Scenario Two: Web Services and Many Community}
    \begin{itemize}        
        \item Based on Coalition Structure theory
        \begin{itemize}    
            \item What coalitions to form? 
            \item Stability in coalition structure, is a partition of players, where no other partition can provide all agents with better utility.
        \end{itemize}
        \item Has to be distributed not centralized
        \item Merge and Split Algorithm
        \begin{itemize}
            \item Iterative
            \item Converges to a final partition
        \end{itemize}
    \end{itemize}
    \begin{figure}[htbp]
        \centering
        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
        \includegraphics[width=0.5 \columnwidth]{figures/scenario2.png}
        %%\includegraphics[scale=0.5]{figure1}
        %\caption{The NetBill payment protocol} \label{figure7}
    \end{figure}       	
\end{frame}

\begin{frame}{Representation and Complexity issues}
    \begin{itemize}
        \item Core and Shapley value are combinatorial problems.
        \item Input size is exponential.
        \item Compact or succinct representation of coalition games. A representation so that the input size is a polynomial in the number of agents.
    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Induced subgraph games}
    \begin{itemize}
        \item An induced subgraph game is a coalitional game defined by an undirected weighted graph $G = (V,W)$ where $V$ is the set of vertices and $W : V \rightarrow V$ is the set of edges weights. For $(i,j) \in V^2$, $w_{ij}$ is the weight of the edge between $i$ and $j$.
        \item $N = V$
        \item for all $C \subseteq N, v(C) = \sum_{(i,j) \in C} w_{ij}$
        \item {\color{red}Space Complexity:} Using an adjacency matrix, we need to provide $n^2$ entries.
        \item {\color{red}Convexity:} If all the weights are nonnegative then the game is convex.
        \item {\color{red}Shapley Value:} $\phi_i(N,v) = \frac{1}{2} \sum_{(i,j) \in N^2 | i \neq j}w_{ij}$
        \item This is {\color{red}not complete}. Many TU games cannot be represented by a induced subgraph game

    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame26 Contribution and Research Activities %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Preliminary Results}
\begin{frame}{Preliminary Results}

    \begin{figure}[!t]
    \centering
    %\includegraphics[scale=0.6]{graph1Final+.eps}
    \includegraphics[width=2.1in]{figures/task_done_opt.pdf}
    \includegraphics[width=2.1in]{figures/task_qos_opt.pdf}
    \caption{Part (a): Cumulative number of requests successfully
    done. Part (b): Average QoS of requests performed.}
    \label{performanceall}
    \end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Preliminary Results}
    \begin{figure}[!t]
        \centering
        %\includegraphics[scale=0.6]{graph1Final+.eps}
        \includegraphics[width=3in]{figures/least_core.pdf}
        \caption{Analysis of \emph{$\epsilon$-core} set non-emptiness, for different values of $\epsilon$} \label{f_leastcore}
    \end{figure}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Preliminary Results}
    \begin{figure}[!t]
        \centering
        %\includegraphics[scale=0.6]{graph1Final+.eps}
        \includegraphics[width=2.1in]{figures/s2_task_done.pdf}
        \includegraphics[width=2.1in]{figures/s2_task_qos.pdf}
        \caption{Part (a): Cumulative number of tasks succesfully done. Part
        (b): Average QoS of tasks performed.} \label{performancemany}
    \end{figure}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Preliminary Results}
    \begin{figure}[!t]
        \centering
        %\includegraphics[scale=0.6]{graph1Final+.eps}
        \includegraphics[width=1.45in]{figures/avg_task_ws_done.pdf}
        \includegraphics[width=1.45in]{figures/avg_qos_ws_done.pdf}
        \includegraphics[width=1.45in]{figures/avg_avail_ws_done.pdf}
        \caption{A comparison between our community model and the high availability community model, on communities of size 4,5,6 only. Part (a): Cumulative number of tasks succesfully done. Part
        (b): Average QoS of tasks performed. (c) Average Community Service Availability} \label{fig_avail_method}
    \end{figure}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame30 outline page
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Milestones}
\begin{frame}{Milestones}
    \begin{itemize}
     	\itemsep=.5cm
    	\item Introduction
    	\item Background and Literature Review
    	\item Proposed Research
    	\item {\bf Time Line}
    \end{itemize}
\end{frame}
